---
title: "SVM With Loan Data"
author: "Krishna P Koirala"
date: "6/25/2018"
output:
    md_document:
     variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
rm(list = ls())
loans <- read.csv("~/Desktop/Data Science with R, Python, SQL, Tableau/Data Science with R, Python --Udemy/Data Science with R/R-Course-HTML-Notes/R-for-Data-Science-and-Machine-Learning/Training Exercises/Machine Learning Projects/CSV files for ML Projects/loan_data.csv")
```


```{r}
str(loans)
```

```{r}
summary(loans)
```

# Change the data types of few columns to factor

```{r}
unique(loans$credit.policy)
unique(loans$inq.last.6mths)
unique(loans$delinq.2yrs)
unique(loans$pub.rec)
unique(loans$not.fully.paid)
```


# Convert to above variables to Categorical

```{r}
loans$credit.policy <- factor(loans$credit.policy)
loans$inq.last.6mths <- factor(loans$inq.last.6mths)
loans$delinq.2yrs <- factor(loans$delinq.2yrs)
loans$pub.rec <- factor(loans$pub.rec)
loans$not.fully.paid <- factor(loans$not.fully.paid)
```


# EDA

```{r}
library(ggplot2)
p1 <- ggplot(aes(fico), data = loans) + geom_histogram(aes(fill = not.fully.paid), color = 'black', bins = 40, alpha = 0.5) + theme_classic()
p1
```

# Histogram with my image on background


```{r}
image <- jpeg::readJPEG("~/Desktop/IMG_0458.JPG")
```

```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(jpeg, png, ggplot2, grid, neuropsychology)
```



```{r}
ggplot(aes(fico), data = loans) +
  ggtitle("Histogram with background")+
  annotation_custom(rasterGrob(image, 
                               width = unit(1,"npc"), 
                               height = unit(1,"npc")), 
                               -Inf, Inf, -Inf, Inf) +
    geom_histogram(aes(fill = not.fully.paid), bins = 40, color = 'black', alpha = 0.1) + scale_fill_manual(values = c('green', 'red'))
```


```{r}
ggplot(aes(factor(purpose)), data = loans) + geom_bar(aes(fill = not.fully.paid), position = 'dodge') + theme_classic()
```


```{r}
ggplot(aes(int.rate, fico), data = loans) + geom_point(aes(color = not.fully.paid), alpha = 0.5)
```

# Using RcolorBrewer


```{r}
library(RColorBrewer)
  ggplot(aes(int.rate, fico, color = not.fully.paid), data = loans) + 
  geom_jitter(alpha = 1, size = 3/4) + scale_color_brewer(type = "div", 
  palette = 7, direction = 1, 
guide = guide_legend(title = 'not fully paid', reverse = TRUE, 
                     override.aes = list(alpha = 1, size = 2))) + theme_dark() + 
      ylab("Fico score") + xlab("Interest rate")
```


# SVM model Building

# Train/Test split

```{r}
# not.fully.paid is the column we are trying to predict
# filter is similar to subset()
library(dplyr)
library(caTools)
set.seed(101)
sample <- sample.split(loans$not.fully.paid, 0.7)
train <- filter(loans, sample == TRUE)
test <- filter(loans, sample==FALSE)
```


# Train the model 

```{r}
library(e1071)
model<- svm(not.fully.paid ~., data = train)
summary(model)
```

# predict the test data 

```{r}
#head(test[1:13])
test$predicted <- predict(model, test)
table(test$predicted, test$not.fully.paid)

```

# Model Tuning


This confusion matrix gives really bad results.
We need to tune the model by playing with 
values of C and Y to make model nice.

```{r}
# This is the way to find out best C and Y pair for the model.
# It takes time. 
tune.result <- tune(svm, train.x = not.fully.paid~., data = train, kernel = 'radial', ranges = list(cost = c(100, 200), gamma = c(0.1)))

summary(tune.result)
```

The error is quite low. We can play around the value of c and Y to make error more low.
But for now we choose this is the best model and move forward.

Now we gonna use C = 100, Y  =0.1 to make our tuned model

```{r}
tuned.model <- svm(not.fully.paid ~., data = train, cost = 100, gamma = 0.1)
```

```{r}
summary(tuned.model)
```

# Predict test data using tuned model

```{r}
test$tuned.prediction <- predict(tuned.model, test)
table(test$tuned.prediction, test$not.fully.paid)
```


```{r}
# Accuracy
accuracy = (102+2179)/(2179+102+234+358)
accuracy
precision = (102)/(358+102)
precision
Recall = (102)/(102+234)
Recall
```


We can change value of C and Y 
and again check acuraccy etc according to the need
of our business. What metric should increased depends
on the need of business.
